The Implications of Disk Oscillations for Dynamical Analysis in the \textit{Gaia} Era

### 2019-06-30 paper/ms.tex
Add calc of total energy error

>>>>

\textbf{Because the energies in the radial and vertical coordinates are related to the
radial and vertical actions by a constant
(Equation~\eqref{eq:JR_Jz_epi_energy}), the fractional error on these two
energies in the as in the actions. The energy in the azimuthal coordinate can
be readily computed, and we therefore conclude that for the given offsets the
error on the total computed energy is
\beq\label{eq:error_total_energy}
\frac{\Delta E}{E} = \frac{\Delta J_R}{J_R} + \frac{\Delta J_{\phi}}{J_{\phi}}
                     + \frac{\Delta J_z}{J_z}\text{.}
\eeq}
